Challenges in Developing Great Quasi-Monte Carlo Software

### 2023-03-17 MCQMC2022ChallengesQMCSoftwareArticle.tex
2023 Mac 14 Updates
Updates from Overleaf

@@

\abstract{
Quasi-Monte Carlo (QMC) methods have developed over several decades. With the explosion in computational science, there is a need for great software that implements QMC algorithms. We summarize the  QMC software that has been developed to date, propose some criteria for developing great QMC software, and suggest some steps toward achieving great software. \SCComment{We demonstrate these criteria and steps in practice with Quasi-Monte Carlo Python library (QMCPy), an open-source community software framework, extensible by design with common programming interfaces to an increasing number of existing or emerging QMC libraries developed by the greater community of QMC researchers.}
}

>>>>

%%%%%%% Author sign off on this first submission, last revision
% Sou-Cheng Choi signed off on
% Yuhan Ding signed off on
% Fred J. Hickernell signed off on
% Jagadeeswaran Rathinavel signed off on
% Aleksei Sorokin signed off on

@@

\abstract{
Quasi-Monte Carlo (QMC) methods have developed over several decades. With the explosion in computational science, there is a need for great software that implements QMC algorithms. We summarize the  QMC software that has been developed to date, propose some criteria for developing great QMC software, and suggest some steps toward achieving great software.  We illustrate these criteria and steps in practice with Quasi-Monte Carlo Python library (QMCPy), an open-source community software framework, extensible by design with common programming interfaces to an increasing number of existing or emerging QMC libraries developed by the greater community of QMC researchers.
}
